%-------------------------
% Resume in Latex
% Author : AlgoUniversity
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\color{BrickRed}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{BrickRed}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
  {\Huge \scshape Syed Ali} \\ \vspace{5pt}
  \small \raisebox{-0.1\height}\faPhone\ +91 9838794319~ \href{mailto:syedaliulhasan19@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{syedaliulhasan19@gmail.com}} ~
  \href{www.linkedin.com/in/syedali237}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}}  ~
  \href{https://github.com/syedali237}{\raisebox{-0.2\height}\faGithub\ \underline{Github}}
  \vspace{-8pt}
\end{center}

\vspace{-12pt}
%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Zakir Husain College Of Engg. \& Tech., AMU}{2022 - 2026}{Bachelor Of Technology in Mech. Engg.}{7.696/10 CGPA}
\resumeSubHeadingListEnd
\vspace{-9pt}



% -----------EXPERIENCE-----------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Branding360}{Oct 2023 -- Nov 2023}
{Front-End Developer Intern}{Lucknow, India}
\resumeItemListStart
\resumeItem{Leveraged \textbf{ReactJS} to develop engaging and interactive user interfaces, combining with \textbf{TailwindCSS} for seamless styling and layout design for creating impactful \textbf{frontends} tailored specifically for local businesses, ensuring a
visually appealing and user-friendly online presence.}
\resumeItem{Implemented a modern and intuitive design that enhanced the brand's online presence and improved user experience.}
\resumeItemListEnd
\resumeSubheading
{CodeChef ZHCET Chapter}{Nov 2023 -- Present}
{Web Developer}{Aligarh, India}
\resumeItemListStart
\resumeItem{Developed and maintained website for the Code Chef Chapter at our university.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-13pt}



%-----------PROJECTS-----------
\section{Projects}
\vspace{-5pt}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{CareSync - Community Health Resource Platform}}{\href{https://github.com/syedali237/CareSync}{\underline{Source Code}}}
\resumeItemListStart
\resumeItem{Developed a comprehensive Healthcare Resource Platform with \textbf{NodeJS} for efficient server-side development with
\textbf{MongoDB} as the database. Integrated \textbf{OAuth} User Authentication.}
\resumeItem{Integrated \textbf{OpenAI API} for Personalized AI Health Consultations and \textbf{Google Maps API} for locating nearby
healthcare resources, enhancing user access to information and appointment bookings}
\resumeItemListEnd
\vspace{-14pt}
\resumeProjectHeading{
\textbf{BookNow - Hotel Booking App }
}{\href{https://github.com/syedali237/BookingApp}{\underline{Source Code}}}
\resumeItemListStart
\resumeItem{Utilized \textbf{TypeScript }for developing the backend REST API using \textbf{NodeJS} and \textbf{MongoDB} as the database storage. 
Designed and developed the frontend using \textbf{ReactJS}. 
}
\resumeItem{Integrated \textbf{JWT} User Authentication.}
\resumeItemListEnd
\vspace{-14pt}
\resumeProjectHeading{\textbf{Real-Time Web Chat Application}}{\href{https://github.com/syedali237/chatapp}{\underline{Source Code}}}
\resumeItemListStart
\resumeItem{Developed the backend runtime environment using \textbf{NodeJS }for efficient server-side development. Utilized \textbf{Express.js }as the web application framework for streamlined routing and middleware functionality. Integrated \textbf{Socket.io }to enable real-time bidirectional communication between clients and the server. 
}
\resumeItemListEnd
\vspace{-14pt}
\resumeProjectHeading{\textbf{Tic Tac Toe Game with Minimax Algorithm}}{\href{https://github.com/syedali237/tic-tac-toe_with_minimax_alg}{\underline{Source Code}}}
\resumeItemListStart
\resumeItem{Designed a Tic Tac Toe game to demonstrate the application of the Minimax algorithm for AI decision-making.}
\resumeItem{Implemented the \textbf{Minimax algorithm} to create an unbeatable AI opponent.}
\resumeItem{Developed a responsive and user-friendly interface using \textbf{ReactJS}.}
\resumeItemListEnd
\vspace{-14pt}

\resumeSubHeadingListEnd
\vspace{2pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item{
        \textbf{Languages}{: Java, JavaScript, Python } \\
        \textbf{Backend}{: Node.js, Express.js}\\
        \textbf{Frontend}{: React, NextJS, TailwindCSS, HTML, CSS, Bootstrap} \\
        \textbf{Clouds \& Databases}{: AWS, PostgreSQL, MongoDB} \\
        \textbf{Web Technologies}{: Docker, Socket.IO} \\
        \textbf{Developer Tools}{: Postman, VS Code, Git/GitHub, IntelliJ} \\

        }
\end{itemize}
\vspace{-13pt}

\section{Leadership Experience}

\resumeSubHeadingListStart
\resumeSubheading
{IEEE STB, ZHCET, AMU}{May 2023 -- Present}
{Joint Secretary}{Aligarh, India}
\resumeItemListStart
\resumeItem{Overseeing administrative functions, event coordination, and member management.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-5 mm}


\section{Algorithmic Competitions/Achievements}
\resumeItemListStart
\resumeItem{Secured \textbf{Top 5} in AMURoboclubs Software Hackathon among 40 teams.}
\resumeItem{Solved \textbf{150+} problems on \textbf{LeetCode}.}
\resumeItem{Selected as a Mentee at \textbf{Women In Tech} - Delhi NCR Chapter}

\resumeItemListEnd

\end{document}
